### 2018-05-04 Docs/runtime_parameters/runtime_parameters.tex
another latex fix

\rowcolor{tableShade}
\verb= burner_threshold_cutoff = &  Mass fraction cutoff for burner\_threshold\_species  used in burner threshold & 1.d-10 \\
\verb= burner_threshold_species = &  Name of the species to be used in burner threshold & "" \\
\rowcolor{tableShade}
\verb= burning_cutoff_density = &  Burning cutoff density (do not burn if density is below this threshold) Initialized to zero, runtime_init() in probin.f90 will check to see if burning_cutoff_density < 0 and if so will set burning_cutoff_density = base_cutoff_density & -1.0d0 \\
\verb= do_burning = &  turn on (.true.) or off (.false.) burning & .true. \\
\rowcolor{tableShade}
\verb= do_subgrid_burning = &  break a zone into subzones, call the burner in each subzone and then average the result to the original cell & .false. \\
\verb= reaction_sum_tol = &  mass fraction sum tolerance (if they don't sum to 1 within this tolerance, we abort) & 1.d-10 \\

>>>>

\rowcolor{tableShade}
\verb= burner_threshold_cutoff = &  Mass fraction cutoff for burner\_threshold\_species  used in burner threshold & 1.d-10 \\
\verb= burner_threshold_species = &  Name of the species to be used in burner threshold & "" \\
\rowcolor{tableShade}
\verb= burning_cutoff_density = &  Burning cutoff density (do not burn if density is below this threshold) Initialized to zero, runtime\_init() in probin.f90 will check to see if burning\_cutoff\_density < 0 and if so will set burning\_cutoff\_density = base\_cutoff\_density & -1.0d0 \\
\verb= do_burning = &  turn on (.true.) or off (.false.) burning & .true. \\
\rowcolor{tableShade}
\verb= do_subgrid_burning = &  break a zone into subzones, call the burner in each subzone and then average the result to the original cell & .false. \\
\verb= reaction_sum_tol = &  mass fraction sum tolerance (if they don't sum to 1 within this tolerance, we abort) & 1.d-10 \\
